Lyman-alpha spectra from rotating outflows

### 2017-11-02 paper/paper.tex
changing style of present plots, about to add new

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{$\tau_{\mathrm{H}}$}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

We evaluate first the effects of increasing rotational
velocity at fixed values of the optical depth and outflow velocity.
Figure \ref{fig:varying_rotation} summarizes the information.
All plots correspond to the same outflow velocity of $\vout=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

% Esta figura deberia tener 3 x 3 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vrot=0, | tau=1E5, vrot=50, | tau=1E5, vrot=100, 
% |tau=1E6, vrot=0, | tau=1E6, vrot=50, | tau=1E6, vrot=100, 
% |tau=1E7, vrot=0, | tau=1E7, vrot=50, | tau=1E7, vrot=100, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_rotation}
	\end{center}
	\caption{\textbf{Caption:} Caption.
	\label{fig:varying_rotation}}
\end{figure*}

@@

% Esta figura deberia tener 3 x 3 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vout=25, | tau=1E5, vout=50, | tau=1E5, vout=75,
% |tau=1E6, vout=25, | tau=1E6, vout=50, | tau=1E6, vout=75,
% |tau=1E7, vout=25, | tau=1E7, vout=50, | tau=1E7, vout=75, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_outflow}
	\end{center}
	\caption{\textbf{Caption:} Caption.
		\label{fig:varying_outflow}}
\end{figure*}

@@

% Esta figura deberia tener 3 x 2 viñetas. tau=10E6.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Caption:} Caption. Tau 10E6.
    \label{fig:doppler_shift}}
\end{figure*}

In order to compare the line creative with the radiative transfer process that 
involves the rotation (RT) and the line with only outflows that is Doppler 
shifted (DS), we calculate three main characteristics for each spectrum. We 
measure the line's mean velocity, standard deviation and skewness for both 
RT and DS approaches. We plot the results for each value in Figures 
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness}, 
respectively for the same \tauh as Figure \ref{fig:doppler_shift}.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/mean_line_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:mean_line}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/standard_deviation_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and 
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/skewness_6}
	\end{center}
	\caption{\textbf{Caption:} The dots represent the Radiative Transfer and 
		the lines represent the Doppler Shift. Tau 10E6.
		\label{fig:skewness}}
\end{figure*}

@@

@@

\subsection{Theoretical Insights}

@@

@@

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode\mathrm \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

We evaluate first the effects of increasing rotational
velocity at fixed values of the optical depth and outflow velocity.
Figure \ref{fig:varying_rotation_small} summarizes the information.
All plots correspond to the same outflow velocity of $\vout=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

% Esta figura deberia tener 2 x 2 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% | tau=1E5, vrot=50, | tau=1E5, vrot=100 |
% | tau=1E6, vrot=50, | tau=1E6, vrot=100 | 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_rotation_small}
	\end{center}
	\caption{\textbf{Spectra for fixed outflow velocity:} We fixed $\vout=50$\kms. 
			 We vary \vrot increasing from left to right, \tauh increasing from top to 
			 bottom, and $\theta$ according to the legend.
	\label{fig:varying_rotation_small}}
\end{figure*}

@@

% Esta figura deberia tener 2 x 2 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% | tau=1E5, vout=25, | tau=1E5, vout=75 |
% | tau=1E6, vout=25, | tau=1E6, vout=75 |
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/results/varying_outflow_small}
	\end{center}
	\caption{\textbf{Spectra for fixed rotational velocity:} We fixed $\vrot=50$\kms. 
			 We vary \vout increasing from left to right, \tauh increasing from top to 
			 bottom, and $\theta$ according to the legend.
		\label{fig:varying_outflow_small}}
\end{figure*}

@@

% Esta figura deberia tener 3 x 2 viñetas. tau=10E6.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.90\textwidth]{./figures/results/doppler_shift_6}
  \end{center}
  \caption{\textbf{Doppler shift effect:} We fixed $\tauh=10^6$ and $\theta=?$. 
  	We vary \vrot increasing from left to right and \vout increasing from top to 
  	bottom. The legend represents the \lya line obtained if there is no rotation 
  	(in thin line), if there is a radiative transfer of rotation and outflows 
  	(thick and clear line), and if there is a radiative transfer of only outflows,
  	but also a Doppler shift from the rotational velocity (thick and dark line). 
	    \label{fig:doppler_shift}}
\end{figure*}

In order to compare the line created with the radiative transfer process that 
involves the rotation (RT) and the line with only outflows that is Doppler 
shifted (DS), we calculate three main characteristics for each spectrum. We 
measure the line's mean velocity, standard deviation and skewness for both 
RT's and DS's approaches. We plot the results for each value in Figures 
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness}, 
respectively for the same \tauh as Figure \ref{fig:doppler_shift}.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/mean_line_7}
	\end{center}
	\caption{\textbf{Mean line for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:mean_line}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/standard_deviation_7}
	\end{center}
	\caption{\textbf{Standard Deviation for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/skewness_7}
	\end{center}
	\caption{\textbf{Skewness for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:skewness}}
\end{figure*}

@@

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the 
valley for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity} 
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=75$\kms and rotation velocity of $\vrot=50$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/valley_intensity}
	\end{center}
	\caption{\textbf{Caption:} We fixed $\vout=75$\kms and $\vrot=50$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

\subsection{Theoretical Insights}
Talk about radiative transfer...

Regarding de Doppler shift... By this logic then, the quality and accuracy of 
the spectrum, obtained by a Doppler shift, increases with the optical depth \tauh. 
This because the more \tauh, the more anisotropic is the photons' distribution 
at the galaxy's border.

The introduction of rotation in the model implies that it will only affect 
galaxies with its viewing angle

@@

Kulas...

MUSE...

@@

\appendix

\section{Additional figures}
\label{sec:appendix}

In this appendix we show Figures \ref{fig:varying_rotation} and \ref{fig:varying_outflow} with more combinations of \vrot and \vout.

% Esta figura deberia tener 3 x 3 vinetas. vout=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vrot=0, | tau=1E5, vrot=50, | tau=1E5, vrot=100, 
% |tau=1E6, vrot=0, | tau=1E6, vrot=50, | tau=1E6, vrot=100, 
% |tau=1E7, vrot=0, | tau=1E7, vrot=50, | tau=1E7, vrot=100, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/appendix/varying_rotation}
	\end{center}
	\caption{\textbf{Caption:} $\vout=50$\kms.
		\label{fig:varying_rotation}}
\end{figure*}

% Esta figura deberia tener 3 x 3 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% |tau=1E5, vout=25, | tau=1E5, vout=50, | tau=1E5, vout=75,
% |tau=1E6, vout=25, | tau=1E6, vout=50, | tau=1E6, vout=75,
% |tau=1E7, vout=25, | tau=1E7, vout=50, | tau=1E7, vout=75, 
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.90\textwidth]{./figures/appendix/varying_outflow}
	\end{center}
	\caption{\textbf{Caption:} $\vrot=50$\kms.
		\label{fig:varying_outflow}}
\end{figure*}
